Learning how to act: making good decisions with machine learning

### 2017-07-28 thesis/offcuts_chapter6.tex
adds draft introduction, moves captions to below figures

>>>>

We can also view causal inference problems as a particular form of transfer learning. We have training data obtained from one system, and wish to use it to estimate characteristics or make predictions about another, in this case the original system after some intervention. To do this we must make some assumptions about the relationship between the two systems. If they are arbitrarily different then information about the first one is not transferable to the second.

I hope these examples give a feel for the richness and subtitles of causal problems. causal inference. We will return to some of them in more detail once we have established some more concrete language and tools to approach them with.

We will call data sets where we do not have control over the decision making process that generated the data observational. Versus experimental data sets, where we do have control (experimental data sets do not always have to be randomised - although that is a powerful approach to ensure we have control. There is a space in the middle where we have partially controlled the process by which agent select actions. Randomised data with imperfect compliance would be an example.
